Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2019-08-03 review/review_response.md

The manuscript in its current form, however, is not at the standards of publication, and requires major revision.  General and specific suggestions are outlined below, and the authors are strongly encouraged to take these comments into account when making revisions to their article.

--------------
Main critiques
--------------

The primary critique of this paper is that it is far too long given its minimal scientific outcomes. This is due to a combination of tedious and redundant text that adds little to the main points of the paper; and a significant fraction of the paper referring to a method which is never deployed due to the limitations of the dataset.  Some specific suggestions:

(1) remove all references to the "shifted subtraction" method, including Section 4 and Appendix A. This method is not used, and the authors' long exposition in section 7.2.2 on the need to schedule observations across semesters is irrelevant given that it is of course possible to request observations across semesters (many ESO programs do this); this section should also be removed. 
**Removed. I have kept one reference to the original motivation.**

(2) Appendix B should also be removed; the methods described here are standard error propagation methods and the definition of the magnitude, and do not need to be reproduced (the footnote to the authors' flux ratio tool could be moved to the main text).
**Removed**

@@

(4) Remove paragraphs that describe in detail multiple fits (e.g. section 6.1). These can be summarized in the Tables and general outcomes discussed.

(5) Please do a critical edit (or ask an editor to do so) to remove redundant/repeated phrases, address grammar issues (there are many places where articles such as "a" and "the" are missing, and dropped phrases), and re-organize some subsections of the paper (some suggestions are below).

In terms of analysis, I have the following concerns:

section 3.1.1 - the description of the use of rectangular vs optimal extraction is both verbose and hard to understand. Please simplify by simply stating (if this is correct) - you extracted the spectra with both techniques, used optimal as the default, but replaced with rectangular when noise features skewed the optimal extraction (NB: this shouldn't happen, which suggests something is wrong with the way the optimal extraction profile is being determined)
**I have simplified this section**

@@

section 7.2.1
the start of this section is completely redundant with a paragraph in the introduction. please consolidate.

section 8
paragraphs 1, 2 and 5 could be removed with no loss of content

Table 1
- reference 8 should be "Gaia Collaboration"

Table 2
- the listed parameters need to be defined in the table caption

- should gamma have units of km/s?
**Yes this has been ammended.**

### 2019-08-03 nir_companions.tex
less verbose artefact removal

There are two types of extraction commonly used. The \emph{rectangular} extraction performs a rectangular aperture sum in the spatial direction while the \emph{optimal} extraction~\citep{horne_optimal_1986} also includes variance weighting to reduce the impact of the noise and deviant pixels on the total flux measurement. {The extracted nod-cycle spectra are normalized by dividing each by a polynomial fitted to the continuum.}

At this point one would normally combine all the optimally extracted nod spectra together to improve the signal-to.noise. {However, we discovered extended artefacts in the optimally reduced nod spectra. We were not able to identify why these artefacts are large and extended but they occur near the presence of a large cosmic rays or bad pixel spike seen in the rectangular extraction. These artefacts were not observed in previous works using this pipeline in the \textit{H}-band, so there may be a wavelength dependent affect. The variance weighting procedure during the optimal extraction is somehow being heavily affected by these spikes.} An example of this can be seen in Fig.~\ref{fig:nod_artefacts} where a spike in the rectangular extraction corresponds to the large extended features in the optimal extraction. The amplitude of these artefacts created flux deviations in the combined optimally extracted spectra up to \(\sim\)0.5 per cent.
{\bl Therefore, we took measures to remove these artefacts before combining the nod spectra}. {Parameters of the pipeline were adjusted to try and remove these artefacts, such as the $\sigma$ rejection limits and the aperture width with limited success. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts.}

The individual spectra from each nodding cycle were visually compared to check for and remove any spectral artefacts. An exampled is shown in Fig.~\ref{fig:nod_artefacts}. The "optimally" extracted nods (top panel) that contained artefacts were replaced with their counter-parts which used the rectangular extraction method (middle panel). An iterative 4-\(\sigma\) rejection algorithm\footnote{Found at \url{https://github.com/jason-neal/nod_combination}} was applied to the replacement spectra to remove the erroneous pixels that created the artefacts in the "optimal" extraction. The \(\sigma\) value for each pixel was calculated as the standard deviation of the nearest 2 pixels on either side of all 8 nod spectra. The rejected pixels were replaced using linear interpolation along the dispersion axis. {Out of the 544 nod spectra from individual detectors, 79 (14 per cent) contained artefacts and were replaced using this technique.}

For the remainder of this paper we use a combined spectra constructed by averaging the 8 nod-cycle spectra where some of the optimally extracted spectra may have been replaced using the above method. The last panel of Fig.~\ref{fig:nod_artefacts} shows an example of a combined spectra and the difference compared to an averaged "optimal" spectrum.

The continuum normalization and nod combining steps were also performed using \textsc{iraf} while the following post reduction procedures and analysis all utilize \textsc{python}. This pipeline was chosen over the ESO CRIRES pipeline because it seemed relatively simple to use, being semi-automated, and initially appeared to have less bad pixel/cosmic ray artefacts in the extracted spectra at first. In hindsight the emergence of the spectral artefacts increased the difficulty of it's use.

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2}\) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters. The \(\chi^{2}\) is defined as
\begin{equation}
\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\bl {\sigma}_{i}^{2}}\,,
\end{equation}
  where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in~\citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500. These values are similar to the those given in Table~\ref{tab:observations} which were calculated from the continuum of detector 2 only.}

@@

\begin{equation}
\rm C^{1}_{i}(\lambda) = J(\lambda_0(1-\frac{{rv}_1}{c}))
\end{equation}

@@

This single component model analysis is similar to the~\citet{passegger_fundamental_2016} \(\chi^2\) fitting. We apply the same re-normalization (see Sect.~\ref{subsec:renorm}) to account for slight differences in the continuum level and possible linear trends between the normalized observation and model. We do not, however, apply any dynamical masking to sensitive lines to make the the \(\chi^2\) minima more distinct or linearly interpolate the stellar parameters between the grid models to obtain high precision stellar parameters. This is because we are not trying to derive precise stellar parameters but to detect the spectra of the companions. We instead include radial velocity components to the \(\chi^2\) fitting, which is not included in~\citet{passegger_fundamental_2016}.

>>>>

Each spectra was extracted twice using the \emph{rectangular} and \emph{optimal} extraction algorithms.
The \emph{rectangular} extraction performs a rectangular aperture sum in the spatial direction while the \emph{optimal} extraction~\citep{horne_optimal_1986} also includes variance weighting to reduce the impact of the noise and deviant pixels on the total flux measurement. {The extracted nod-cycle spectra are normalized by dividing each by a polynomial fitted to the continuum.}

The average of the 8 nod-cycle spectra was used to create a combined spectra with a higher signal-to-noise.
Where possible the 8 optimally extracted spectra were combined, but several nod spectra were replaced with their rectangular counterparts because spectral artefacts were visually identified in the \emph{optimal} nod spectra. For the replacement nods, a iterative 4-\(\sigma\) rejection algorithm\footnote{Found at \url{https://github.com/jason-neal/nod_combination}} was applied to remove the bad pixels that were not removed in the \emph{rectangular} extraction.

An example of a large extended artefact is given in Fig.~\ref{fig:nod_artefacts}. The top and middle panels show the the 8 normalized nod spectra for the \emph{optimal} and \emph{rectangular} methods respectively. In the top panel there is a clear deviation in the seventh nod spectra around pixel 200, which corresponds to a spike in the middle panel. The bottom panel shows the difference in the combined average spectra, between using only the optimal spectra and replacing those with artefacts, in this case the seventh spectrum. These artefacts were observed to create flux deviations in the combined spectra up to \(\sim\)0.5 per cent.

These artefacts had not been observed in previous works using this pipeline in the \textit{H}-band, so this may be a wavelength dependent affect.
Several parameters of the reduction pipeline were adjusted in an attempt to  remove these artefacts with limited success, e.g. the $\sigma$ rejection limits and the aperture width. In a small number of instances allowing the aperture width to be automatically adjusted removed the artefacts.

The continuum normalization and nod combining steps were also performed with \textsc{iraf} while the following post reduction procedures and analysis utilize \textsc{python}. This pipeline was chosen over the ESO CRIRES pipeline because it was semi-automated, seemed relatively simple to use and, initial tests appeared to contain less bad pixel/cosmic ray artefacts in the extracted spectra compared to the ESO pipeline. In hindsight, the spectral artefacts observed decreased it's ease of use.

@@

\subsection{\texorpdfstring{\(\chi^{2}\)}\ \ method}
\label{subsec:chi2}
The well known \(\chi^{2}\) technique measures the weighted sum of the squared deviation between the observation (\({O}_{i}\)) and the computed models (\(C_{i}\)), with the minimum \(\chi^2\) value representing the best-fit parameters. The \(\chi^{2}\) is defined as
\begin{equation}
\chi^{2} = {\Sigma}_i { (O_{i} - C_{i})}^2 / {\bl {\sigma}_{i}^{2}}\,,
\end{equation}
  where \({\sigma}_{i}\) is the error on each measurement. We estimate the \(\sigma\) of each spectrum using the \(\beta\sigma\) method~\citep{czesla_posteriori_2018}, using the MAD (median absolute deviation about the median) robust estimator. {This method estimates the spectral noise using numerical derivatives of the spectra. We followed the procedure outlined in~\citet{czesla_posteriori_2018}, analysing the results from successive parameter combinations to settle on an order of approximation (derivative level) of 5, and a jump parameter (pixels skipped to avoid correlations) of 2.} We apply the same \(\sigma\) value to all points \({\sigma}_{i} = \sigma\). The \(\beta\sigma\) method provided \(\sigma\) estimates for the target spectra which correspond inversely to signal-to-noise ratios between 100--500. These values are similar to the those given in Table~\ref{tab:observations} which were calculated from the continuum of detector 2 only.

@@

It can be summarized by the equation, 
\begin{equation}
\rm C^{1}_{i}(\lambda) = J(\lambda_0(1-\frac{{rv}_1}{c})),
\end{equation}

@@

This single component model is similar to the \(\chi^2\) fitting performed by \citet{passegger_fundamental_2016}. We apply the same re-normalization (see Sect.~\ref{subsec:renorm}) to account for slight differences in the continuum level and possible linear trends between the normalized observation and model. Unlike \citet{passegger_fundamental_2016} we do not apply any dynamical masking to sensitive lines to make the the \(\chi^2\) minima more distinct or linearly interpolate the stellar parameters between the grid models to obtain high precision stellar parameters. This is due to the differnces in our end goals, detecting a secondary spectral component, compared to deriving precise stellar parameters. We also include radial velocity components to the \(\chi^2\) fitting, which is not included in~\citet{passegger_fundamental_2016}.
